**Density Dependence**

### 2023-03-09 Rmd/mseMac.Rmd
uppity

```{r, pars}
params=FLPar(c(m1=0.15/(0.2^-0.288),m2=-0.288,   bref=3.69e+06,delta=-0.3,     matk=30,      w50=0.17))
params=FLPar(c(m1=9.69e-02         ,m2=-2.88e-01,bref=4.11e+06,delta=-2.00e-01,matk=2.80e+01,w50=1.66e-01)) 
```

@@

```{r, eval=FALSE}
load("~/Desktop/tmp/eqM.RData")
load("~/Desktop/tmp/om..RData")
load("~/Desktop/tmp/oms..RData")
load("~/Desktop/tmp/prj..RData")
load("~/Desktop/tmp/prjs..RData")

@@

eqCurves=ldply(oms., function(x) { 
    model.frame(FLQuants(x[,dim(oms[[1]])[2]],
                         biomass=function(x) stock(x),
                         ssb    =function(x) ssb(  x),
                         catch  =function(x) catch(x),
                         f      =function(x) fbar( x)),drop=TRUE)[,-1]})
ts=ldply(prj., function(x) model.frame(FLQuants(x, ssb  =function(x) ssb(  x), 
                                                  f    =function(x) fbar(x), 
                                                  catch=function(x) catch(x)),drop=T))
ts=transform(ts,What=.id)
ts=transform(ts,.id=unique(eqCurves$.id)[an(iter)])

@@

>>>>

```{r, pars}
params=FLPar(c(m1=0.15/(0.2^-0.288),m2=-0.288,   bref=3.69e+06,delta=-0.3,     matk=30,      w50=0.17))
#params=FLPar(c(m1=9.69e-02         ,m2=-2.88e-01,bref=4.11e+06,delta=-2.00e-01,matk=2.80e+01,w50=1.66e-01)) 
```

@@

```{r, eval=FALSE}
load("~/Desktop/tmp/eqM.RData")
load("~/Desktop/tmp/om..RData")
load("~/Desktop/tmp/oms..RData")
load("~/Desktop/tmp/prj..RData")
load("~/Desktop/tmp/prjs..RData")
load("/home/laurie/Dropbox/DDMSE/results/mac/mac_section5.RData")

@@

eqCurves=ldply(oms., function(x) { 
    model.frame(FLQuants(x[,dim(oms.[[1]])[2]],
                         biomass=function(x) stock(x),
                         ssb    =function(x) ssb(  x),
                         catch  =function(x) catch(x),
                         f      =function(x) fbar( x)),drop=TRUE)[,-1]})
ts=ldply(prj., function(x) model.frame(FLQuants(x,ssb  =function(x) ssb(  x), 
                                                  f    =function(x) fbar(x), 
                                                  catch=function(x) catch(x)),drop=T))
ts=transform(ts,What=.id)
ts=transform(ts,.id=unique(eqCurves$.id)[an(iter)])

fmsy=transform(ddply(eqCurves,.(.id), with, 
                     data.frame(Fmsy=f[catch==max(catch)])),lower=Fmsy*0.8,upper=Fmsy*1.2)
msy=ddply(merge(eqCurves,fmsy,by=".id"),.(.id), with, 
      data.frame(lcatch=catch[min((lower-f)^2)==(lower-f)^2],
                 msy   =catch[catch==max(catch)],
                 ucatch=catch[min((upper-f)^2)==(upper-f)^2]))
bmsy=ddply(merge(eqCurves,fmsy,by=".id"),.(.id), with, 
      data.frame(lssb   =ssb[min((lower-f)^2)==(lower-f)^2],
                 bmsy   =ssb[catch==max(catch)],
                 ussb   =ssb[min((upper-f)^2)==(upper-f)^2]))

ggplot(eqCurves)+
  geom_line(aes(f,catch,col=.id))+scale_x_continuous(limits=c(0,2))+
  theme(legend.position="bottom")

@@

```{r}
load("~/Desktop/tmp/prjs..RData")
load("~/Desktop/tmp/oms..RData")
load("/home/laurie/Dropbox/DDMSE/results/mac/mac_section5.RData")

eqCurves=ldply(oms, function(x) { 
    model.frame(FLQuants(x[,dim(oms[[1]])[2]],
                         biomass=function(x) stock(x),
                         ssb    =function(x) ssb(  x),
                         catch  =function(x) catch(x),
                         f      =function(x) fbar( x)),drop=TRUE)[,-1]})

fmsy=transform(ddply(eqCurves,.(.id), with, 
                     data.frame(Fmsy=f[catch==max(catch)])),lower=Fmsy*0.8,upper=Fmsy*1.2)
msy=ddply(merge(eqCurves,fmsy,by=".id"),.(.id), with, 
      data.frame(lcatch=catch[min((lower-f)^2)==(lower-f)^2],
                 msy   =catch[catch==max(catch)],
                 ucatch=catch[min((upper-f)^2)==(upper-f)^2]))
bmsy=ddply(merge(eqCurves,fmsy,by=".id"),.(.id), with, 
      data.frame(lssb   =ssb[min((lower-f)^2)==(lower-f)^2],
                 bmsy   =ssb[catch==max(catch)],
                 ussb   =ssb[min((upper-f)^2)==(upper-f)^2]))

sch=ldply(prjs, function(x) ldply(x, function(x) { 
    model.frame(FLQuants(x,
                         biomass=function(x) stock(x),
                         ssb    =function(x) ssb(  x),
                         catch  =function(x) catch(x),
                         f      =function(x) fbar( x)),drop=TRUE)}))
sch=transform(sch,.id=factor(.id,labels=c("Base","DD Mass","DD Mass, Mat","DD Mass, Mat, M")))

sch=subset(sch,year==2050)
sch=merge(sch,bmsy,by=".id")
sch=merge(sch,msy,by=".id") 
```

```{r, kobe-base, fig.height=8,fig.width=8}
p1=kobe:::kobePhaseMar2(subset(transmute(subset(sch,.id=="Base"),stock=ssb/bmsy,harvest=catch/msy,run=ac(f))),
                     xlab=expression(B/B[MSY]),ylab=expression(Catch/MSY),col=c("red","grey","grey","grey")) 
```

```{r,kb-m, fig.height=8,fig.width=8}
p2=kobe:::kobePhaseMar2(subset(transmute(subset(sch,.id=="DD Mass"),stock=ssb/bmsy,harvest=catch/msy,run=ac(f))),
                     xlab=expression(B/B[MSY]),ylab=expression(Catch/MSY),col=c("grey","red","grey","grey")) 
```

```{r,kobe-mm, fig.height=8,fig.width=8}
p3=kobe:::kobePhaseMar2(subset(transmute(subset(sch,.id=="DD Mass, Mat"),stock=ssb/bmsy,harvest=catch/msy,run=ac(f))),
                     xlab=expression(B/B[MSY]),ylab=expression(Catch/MSY),col=c("grey","grey","red","grey")) 
```

```{r,kobe-mmm, fig.height=8,fig.width=8}
p4=kobe:::kobePhaseMar2(subset(transmute(subset(sch,.id=="DD Mass, Mat, M"),stock=ssb/bmsy,harvest=catch/msy,run=ac(f))),
                     xlab=expression(B/B[MSY]),ylab=expression(Catch/MSY),col=c("grey","grey","grey","red")) 
```

```{r, den-ssb}
ggdensity(transmute(sch,stock=ssb/bmsy,harvest=catch/msy,run=ac(signif(f,3)),.id=.id),x="stock",fill=".id")+
  geom_vline(aes(xintercept=1),col="red")+
  facet_grid(run~.) 
```

```{r, den-yield}
ggdensity(transmute(sch,stock=ssb/bmsy,catch=catch/msy,run=ac(signif(f,3)),.id=.id),x="catch",fill=".id")+
  geom_vline(aes(xintercept=1),col="red")+
  facet_grid(run~.) 
```
